\section{Efficiency Analysis}
\label{sec:efficiency}

We now quantify the practical overhead of TVS against the savings it yields in downstream video processing. To remain comparable across hardware, API endpoints, and network conditions, we report \textit{hardware-agnostic proxies} that directly determine end-to-end cost in any fixed deployment, and then close the loop under realistic downstream frame budgets.

\paragraph{Cost drivers.}
For each sample we record the number of external LLM turns (\#LLM), tool invocations for caption/visual queries (\#Tool), total captions used (\#TotalCap), and output tokens excluding hidden reasoning tokens (\#OutTok). Screening effectiveness is measured by $\mathrm{DurAll} = \mathbb{E}[|v|/|V|]$ over all samples, $\mathrm{DurScrn}$ the same ratio restricted to successfully screened samples, and $\mathrm{Screen\%}$ the fraction of samples for which $\mathcal{F}_{\mathrm{TVS}}(V,Q) \ne (V,Q)$.

\paragraph{Closing the loop under fixed frame budgets.}
Comparing TVS against a no-TVS baseline purely via the count of downstream frames can be misleading: a fixed budget of $K$ frames sampled uniformly over a long video is extremely sparse and may under-cover the evidence, while the same $K$ frames concentrated on the screened segment yield much denser coverage. We define \textbf{density amplification} and the \textbf{visual cost ratio}
\begin{align*}
\mathrm{DensAmp} &= \mathbb{E}\!\left[\tfrac{1}{\mathrm{DurRatio}}\right], \ \ \mathrm{EquivFr}(K) = K \cdot \mathrm{DensAmp}, \\[-0.2em]
\mathrm{CostRatio}(K) &= \tfrac{K + \mathrm{TotalCap}}{\mathrm{EquivFr}(K)}.
\end{align*}
A lower $\mathrm{CostRatio}$ means TVS achieves the same effective evidence density at a smaller fraction of the dense-sampling cost: e.g., $\mathrm{CostRatio}{=}0.1$ means downstream QA without TVS would incur $10\times$ the frame-sampling cost to match the same evidence density. We also report $\mathrm{OutTok/1\%Red} = \mathbb{E}[\mathrm{\#OutTok}] / ((1{-}\mathbb{E}[\mathrm{DurScrn}]){\cdot}100)$, the output-token cost of each $1\%$ reduction in video duration.

\begin{table*}[t]
  \centering
  \small
  \setlength{\tabcolsep}{4pt}
  \begin{subtable}{\textwidth}
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|cccc|ccc}
      \toprule
      \textbf{Dataset} & \textbf{\#TotalCap} & \textbf{\#Tool} & \textbf{\#LLM} & \textbf{\#OutTok} & \textbf{DurAll} & \textbf{DurScrn} & \textbf{Screen\%} \\
      \midrule
      ActivityNet-QA  & 21.4 & 1.9 & 3.2 & 341  & 9.8\%  & 9.0\%  & 99.2\% \\
      YouCookII-TVS   & 21.9 & 1.9 & 3.3 & 366  & 6.4\%  & 6.4\%  & 100.0\% \\
      NExT-OE         & 23.4 & 3.9 & 5.0 & 433  & 20.2\% & 16.7\% & 95.7\% \\
      EgoSchema       & 22.1 & 2.1 & 3.5 & 446  & 26.0\% & 26.0\% & 100.0\% \\
      LVBench         & 27.0 & 7.0 & 9.6 & 1482 & 2.2\%  & 1.9\%  & 99.7\% \\
      MLVU            & 24.9 & 4.9 & 6.9 & 1122 & 12.2\% & 7.0\%  & 94.4\% \\
      Video-MME       & 23.9 & 3.9 & 5.7 & 806  & 8.3\%  & 8.0\%  & 99.7\% \\
      \bottomrule
    \end{tabular}%
    }
    \caption{ReSimplifyIt-simple}
    \label{tab:cost_simple}
  \end{subtable}

  \vspace{0.3em}
  \begin{subtable}{\textwidth}
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|ccc|ccc}
      \toprule
      \textbf{Dataset} & \textbf{\#TotalCap} & \textbf{V$\rightarrow$Vw} & \textbf{VwTl} & \textbf{DurAll} & \textbf{DurScrn} & \textbf{Screen\%} \\
      \midrule
      ActivityNet-QA  & 67.5 & 2.7 & 6.8  & 51.7\% & 16.2\% & 57.6\% \\
      YouCookII-TVS   & 73.9 & 2.4 & 5.8  & 6.8\%  & 6.8\%  & 97.9\% \\
      NExT-OE         & 18.3 & 0.4 & 1.3  & 86.9\% & 32.8\% & 19.5\% \\
      EgoSchema       & 50.6 & 2.3 & 4.5  & 75.0\% & 25.6\% & 33.6\% \\
      LVBench         & 83.8 & 2.6 & 11.3 & 57.5\% & 4.8\%  & 44.6\% \\
      MLVU            & 64.5 & 1.7 & 5.2  & 81.4\% & 7.2\%  & 20.1\% \\
      Video-MME       & 76.2 & 2.4 & 6.7  & 64.0\% & 10.4\% & 40.1\% \\
      \bottomrule
    \end{tabular}%
    }
    \caption{ReSimplifyIt (full). V$\rightarrow$Vw: Viewer sessions spawned per sample; VwTl: total tool calls made by the Viewer. Full per-source caption breakdown (passive vs.\ active) is reported in Appendix~\ref{appendix:efficiency_full}.}
    \label{tab:cost_full}
  \end{subtable}
  \caption{Per-dataset cost drivers and screening effectiveness for the two TVS instantiations.}
  \label{tab:cost_drivers}
\end{table*}

\paragraph{Screening is lightweight.}
Table~\ref{tab:cost_drivers} shows that ReSimplifyIt-simple requires only ${\sim}22$ captions (of which ${\sim}20$ are pre-loaded at initialization and only ${\sim}2$--$7$ are actively requested through tool calls), 3--10 LLM calls, and 300--1{,}500 output tokens per sample, while achieving a screening success rate of 94.4\%--100\% across all seven benchmarks. The full multi-agent ReSimplifyIt uses more resources due to its iterative refinement, with roughly half of its captions passively embedded in agent prompts and the other half actively fetched via the Viewer's tools. Both variants reduce videos to a small fraction of their original duration on successfully screened samples---down to 1.9\% (simple) and 4.8\% (full) on LVBench---with compression strongest on the longest benchmarks.

\begin{table*}[t]
  \centering
  \small
  \setlength{\tabcolsep}{4pt}
  \begin{subtable}{\textwidth}
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|cc|cccc}
      \toprule
      \textbf{Dataset} & \textbf{DensAmp} & \textbf{OutTok/1\%} & \multicolumn{4}{c}{\textbf{CostRatio}$(K)$} \\
      & & & $K{=}8$ & $K{=}16$ & $K{=}32$ & $K{=}100$ \\
      \midrule
      ActivityNet-QA  & 25.0$\times$  & 3.8  & 0.15 & 0.09 & 0.07 & 0.05 \\
      YouCookII-TVS   & 29.7$\times$  & 3.9  & 0.13 & 0.08 & 0.06 & 0.04 \\
      NExT-OE$^{*}$   & 20.7$\times$  & 5.2  & 0.19 & 0.12 & 0.08 & 0.06 \\
      EgoSchema       & 6.3$\times$   & 6.0  & 0.59 & 0.38 & 0.27 & 0.19 \\
      LVBench         & 320.7$\times$ & 15.1 & 0.01 & 0.01 & 0.01 & 0.00 \\
      MLVU            & 70.6$\times$  & 10.8 & 0.06 & 0.04 & 0.02 & 0.02 \\
      Video-MME       & 51.2$\times$  & 8.8  & 0.08 & 0.05 & 0.03 & 0.02 \\
      \bottomrule
    \end{tabular}%
    }
    \caption{ReSimplifyIt-simple}
    \label{tab:costratio_simple}
  \end{subtable}

  \vspace{0.3em}
  \begin{subtable}{\textwidth}
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{l|cc|cccc}
      \toprule
      \textbf{Dataset} & \textbf{DensAmp} & \textbf{OutTok/1\%} & \multicolumn{4}{c}{\textbf{CostRatio}$(K)$} \\
      & & & $K{=}8$ & $K{=}16$ & $K{=}32$ & $K{=}100$ \\
      \midrule
      ActivityNet-QA  & 65.2$\times$  & 39.6 & 0.18 & 0.10 & 0.06 & 0.03 \\
      YouCookII-TVS   & 14.7$\times$  & 25.5 & 0.70 & 0.38 & 0.23 & 0.12 \\
      NExT-OE$^{*}$   & 12.3$\times$  & 34.9 & 0.83 & 0.45 & 0.27 & 0.14 \\
      EgoSchema       & 25.8$\times$  & 77.3 & 0.67 & 0.36 & 0.20 & 0.09 \\
      LVBench         & 852.8$\times$ & 38.5 & 0.02 & 0.01 & 0.01 & 0.00 \\
      MLVU            & 308.5$\times$ & 48.9 & 0.06 & 0.03 & 0.02 & 0.01 \\
      Video-MME       & 114.5$\times$ & 43.2 & 0.12 & 0.07 & 0.04 & 0.02 \\
      \bottomrule
    \end{tabular}%
    }
    \caption{ReSimplifyIt (full).}
    \label{tab:costratio_full}
  \end{subtable}
  \caption{Density amplification, output-token cost per $1\%$ of video-length reduction, and visual CostRatio under four downstream frame budgets $K$. All statistics are averaged over successfully screened samples. \textsuperscript{*}NExT-OE has a low screening rate, so averages are over a smaller subset of samples and are reported for completeness.}
  \label{tab:costratio}
\end{table*}

\paragraph{Density amplification and end-to-end cost.}
Table~\ref{tab:costratio} quantifies how the screening overhead is repaid by concentrated downstream sampling. ReSimplifyIt-simple achieves $6.3\times$--$320.7\times$ density amplification: on LVBench, $8$ frames sampled from the screened segment are as temporally dense as uniformly sampling $2{,}566$ frames from the full video. The full ReSimplifyIt reaches $12.3\times$--$852.8\times$ on successfully screened samples, with the largest gains on long-video benchmarks (LVBench $852.8\times$, MLVU $308.5\times$). The output-token cost is likewise modest: $3.8$--$15.1$ tokens per $1\%$ of duration reduction for ReSimplifyIt-simple, and $25.5$--$77.3$ for ReSimplifyIt. For reference, compressing an ActivityNet video by $91\%$ costs the simple variant only $341$ output tokens---less than a short paragraph of text. Under the standard downstream budget of $K{=}8$, ReSimplifyIt-simple's $\mathrm{CostRatio}\leq 0.19$ on $6$ of $7$ datasets (LVBench reaching just $0.01$, a ${\sim}100\times$ cost reduction), and the full variant reports $\mathrm{CostRatio}\in[0.02, 0.18]$ on the long-video benchmarks where it is most effective. As $K$ grows to $16, 32, 100$, $\mathrm{CostRatio}$ decreases monotonically across all datasets, indicating that TVS becomes \emph{increasingly} cost-effective as downstream Video-LLMs adopt denser frame sampling.

\paragraph{Takeaway.}
The agentic screening cost is quantitatively modest while its downstream savings scale with video length. Combined with the accuracy gains reported in the previous section, TVS is a practically deployable front-end for long-video question answering, and its three instantiations (Appendix~\ref{ablations}) offer an explicit performance--cost spectrum from which practitioners can choose depending on deployment constraints.
