\section{Formulation of Temporal Visual Screening (TVS)}

\subsection{Task Definition}
\label{tvs_def}
Given a full-length video $V = \{F_1, F_2, \ldots, F_T\}$ of $T$ ordered frames and a natural language query $Q$, the \textbf{Temporal Visual Screening (TVS)} task produces:

\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
    \item a reconstructed query $q$, derived from $Q$, and
    \item a \textbf{continuous} video
    \vspace{-0.3 em}
    \begin{multline*}
    v = \{F_{s_1}, F_{s_1+1}, \ldots, F_{e_1},\ F_{s_2}, F_{s_2+1}, \ldots, \\ F_{e_2},\ \ldots, F_{s_n}, F_{s_n+1}, \ldots, F_{e_n}\} \subseteq V
    \end{multline*}
    formed by concatenating $n$ non-overlapping segments of $V$, with $1 \leq s_1 \leq e_n \leq T$ and $n \geq 1$,
\end{itemize}

\noindent such that $v$ preserves \textit{low-level temporal continuity} essential for motion, spatial, and object-level reasoning, and $(v,q)$ remains sufficient to recover the original answer. We define an endomorphic transformation
\vspace{-0.2 em}
\[
\mathcal{F}_{\text{TVS}} : (V, Q) \rightarrow (v, q)
\]
over the same bimodal task space (Figure~\ref{fig:tvs_task_compare}), subject to the efficacy conditions given below.

\subsection{Information-Theoretic View}
\label{tvs_ib}
We adopt a \textit{generative} view of VideoQA: the answer $A$ is an objective fact that exists independently of any particular framing, and the observed pair $(V, Q)$ is drawn conditional on $A$. TVS further processes $(V, Q)$ into a compact pair $(v, q)$, yielding the Markov chain
\vspace{-0.2em}
\[
A \;\longrightarrow\; (V, Q) \;\longrightarrow\; (v, q),
\]
analogous to measurement invariance in the physical sciences: reformulating the observation does not alter the underlying fact. The data processing inequality thus gives
\vspace{-0.2em}
\[
I\big((v,q);\,A\big) \;\leq\; I\big((V,Q);\,A\big),
\]
with equality iff $(v, q)$ is a \textit{sufficient statistic} for $A$. Combined with the Information Bottleneck principle~\citep{tishby1999information, tishby2015deep}, TVS seeks a compressed bimodal input that retains answer-relevant information while discarding task-irrelevant content:
\vspace{-0.2em}
\[
\mathcal{L}_{\text{IB}}(v,q) \;=\; I\big((v,q);\,A\big) \;-\; \beta \cdot I\big((V,Q);\,(v,q)\big),
\]
where $\beta > 0$ trades answer sufficiency against input compression. In contrast to latent-code IB~\citep{alemi2017deep}, TVS produces an \textit{interpretable artifact} $(v,q)$ in the original input space, which doubles as a controllable handle for downstream reasoning.

\paragraph{Efficacy conditions for TVS}
Maintaining both \textit{uni-modal efficacy} and \textit{cross-modal synergy}, TVS trims insignificant video segments while \textit{synchronously} reconstructing the text query. The transformations applied to $q$ and $v$ must be tightly coupled to preserve answer consistency under input reduction. Formally:

\begin{enumerate}[leftmargin=*,topsep=2pt,itemsep=1pt]
    \item \textbf{Continuity for Video Output}: $v$ must be a temporally \textbf{contiguous} subsegment of $V$, or a concatenation of such segments, preserving low-level visual integrity for tracking motion, appearance, and scene dynamics. \textit{(Structural constraint on the feasible compression space.)}

    \item \textbf{Sufficiency for Answer}: $(v,q)$ must remain a sufficient statistic for $A$,
    \[
    I\big((v,q);\,A\big) \;=\; I\big((V,Q);\,A\big),
    \]
    saturating the data processing inequality. At the frame level, removing any $F_t \in v$ incurs a non-trivial change in model output: $\exists\, \delta a$ s.t.\ $\mathcal{M}(q, v\setminus\{F_t\}) = a + \delta a,\ |\delta a| > \epsilon$, where $\epsilon$ is a task-specific tolerance setting the operating $\beta$.

    \item \textbf{Reasoning Minimality for Query Output}:
    \[
    q^* \;=\; \operatorname*{argmin}_{q} \, \mathrm{Infer}(q),
    \]
    where $\mathrm{Infer}(q)$ counts reasoning steps needed to derive $A$ from visual input (e.g., ``within 5\,s after event A'' takes three: localize A, apply ``after'', bound ``5\,s''). \textit{(Query-side compression: a tractable proxy for reducing $I(Q;q)$, shifting reasoning load from the downstream model to the reconstructed problem.)}

    \item \textbf{Cross-modal Synergy}: for any reasonable VideoQA agent $\mathcal{M}$,
    \[
    \forall \mathcal{M}, \quad \mathcal{M}(q, v) = \mathcal{M}(Q, V).
    \]
    \textit{(Answer invariance across architectures, the behavioral counterpart of sufficiency.)}
\end{enumerate}

\paragraph{Why the Pareto frontier collapses}
A naive reading of conditions 2 and 3 suggests a Pareto trade-off between preserving $A$-sufficiency and minimizing $\mathrm{Infer}(q)$. In practice, the two objectives are not independent: reducing $\mathrm{Infer}(q)$ by stripping query conditions that target a particular portion of the video automatically reduces the span of $V$ that must be retained to remain $A$-sufficient, and vice versa. The two objectives thus decrease in lockstep along the admissible region, and the Pareto frontier typically collapses to a single operating point that ReSimplifyIt (Section~\ref{sec:method}) converges to iteratively.

We stress that this constraint re-allocation is a \textit{mechanism-level account} of why TVS admits a unique optimum, not a redefinition of the task. TVS remains a joint bimodal transformation $\mathcal{F}_{\text{TVS}}: (V, Q) \to (v, q)$ that preserves both the answer and the answer space; it is \textbf{not} query relaxation, since no constraint is discarded---all are conserved across modalities.

\subsection{Integrating TVS into Video-LLM Workflows}

TVS plugs into both training and inference pipelines of video-language models as a front-end adapter.

\paragraph{TVS for Inference-Time Simplification in Video-LLMs} At inference, TVS pre-processes $(V, Q)$ into $(v, q)$ (see Section~\ref{sec:method}), reducing the temporal and semantic complexity the downstream model must handle and concentrating it on compact, task-relevant content for fine-grained temporal reasoning and direct visual grounding.

\paragraph{TVS for Improving Training-Time Visual-Language Alignment}
Video-LLM supervision tuples $(V, Q, a)$ often couple abstract or multi-hop queries with unfocused video. TVS reshapes them into compact triples $(v, q, a)$, where $v$ is a high-utility segment and $q$ is a grounded reformulation of $Q$, offloading off-target supervision to upstream modules so that the model specializes in two core competencies: temporal understanding and multimodal alignment.
